\mireval{}

### 2014-05-09 paper/paper.tex
Revising chord section

% relevant papers
% - pauwels & peeters
% - matthais
% - harte
% - mirex 
% - Utrecht agreement

Despite being one of the oldest MIREX tasks, evaluation methodology and metrics for automatic chord estimation (ACE) is an ongoing topic of discussion, due to issues with vocabularies, comparison semantics, and other lexicographical challenges unique to the task \cite{pauwels2013evaluating}.
%For example, ISMIR 2010 saw the fondly dubbed ``Utrecht Agreement on Chord Evaluation''\footnote{http://www.music-ir.org/mirex/wiki/The\_Utrecht\_Agreement\_on\_Chord\_Evaluation}, in which interested researchers met to discuss sane ways of quantifying the performance of automatic chord estimation systems.
One source of difficulty stems from an inherent subjectivity in ``spelling'' a chord name and the level of detail a human observer can provide in a reference annotation \cite{ni2013understanding}.
As a result, a consensus has yet to be reached regarding the single best approach to comparing two sequences of chord labels, and instead are often compared over a set of rules, i.e Root, Major-Minor, and Sevenths, with or without inversions.

To efficiently compare chords, we first translate a given chord label $\mathcal{C}$ into a numerical representation, based on the syntax of \cite{harte2010towards}.
For example, the chord label \texttt{G:maj(6)/5} is mapped to three pieces of information: one, the root (``G'') is mapped to an absolute pitch class $\mathcal{R}$, in $[0, 11]$, where C $\to0$, C$\sharp$/D$\flat$ $\to1$, etc; two, the quality shorthand (``maj'') and scale degrees (``6'') are mapped to a root-invariant bit vector $\mathcal{S}$ of active semitones; and three, the bass interval (``5'') is translated to the relative scale degree in semitones $\mathcal{B}$.
%Traditionally, extended chords (9's, 11's or 13's) are not considered in evaluation and instead resolved to the tetrad contained therein, e.g. $C:9 \to C:7$, etc. 
%This semitone bit-vector representation can, however, be easily expanded to represent such information in the future.

Based on this representation, we can symbolically define our interpretation of the five rules used in MIREX 2013\cite{choi2013mirex} to compare an estimated chord $\mathcal{C}_{est}$ with a reference $\mathcal{C}_{ref}$.
\textbf{Root} is given by $\mathcal{R}_{est} == \mathcal{R}_{ref}$, for all chords.
\textbf{Major-Minor} includes \textbf{Root}, plus $\mathcal{S}_{est} == \mathcal{S}_{ref}$ subject to $\mathcal{S}_{ref} \in \{Maj, min\}$.
\textbf{Major-Minor-Inv} includes \textbf{Major-minor}, plus $\mathcal{B}_{est} == \mathcal{B}_{ref}$ subject to $\mathcal{B}_{ref} \in \mathcal{S}_{ref}$.
\textbf{Sevenths} follows \textbf{Major-minor}, but is instead subject to $\mathcal{S}_{ref} \in \{Maj, min, Maj7, min7, 7, minmaj7\}$.
Finally, \textbf{Sevenths-Inv} includes \textbf{Sevenths}, plus $\mathcal{B}_{est} == \mathcal{B}_{ref}$ subject to $\mathcal{B}_{ref} \in \mathcal{S}_{ref}$.
Before proceeding, we draw attention to the set-inclusion conditions above, e.g. ``subject to...'', meaning that a comparison is \emph{ignored} during evaluation if the given criteria is not satisfied.

Track-wise scores, $S_n$, are computed by weighting each comparison by the duration of its interval, over all intervals in an audio file; stated another way, this is the piecewise continuous-time integral of the equivalence of two chord sequences, $(\mathbf{C}_{ref}, \mathbf{C}_{est})$, expressed as follows:

\begin{equation}
S_n(\mathbf{C}_{ref}, \mathbf{C}_{est}) = \frac{1}{T}\int_{t=0}^{T} \mathcal{C}_{ref}(t) == \mathcal{C}_{est}(t)
\end{equation}

\noindent This is achieved by forming the union of the boundaries in each sequence, and summing the time intervals of the ``correct'' ranges. 
The cumulative score, referred to as \emph{weighted chord symbol recall} (WCSR), is tallied over a set of $N$ items, i.e. audio files, by discrete summation, where the importance of each score, $S_n$, is weighted by the duration, $T_n$, of each annotation:

\begin{equation}
WCSR_{total} = \frac{\sum_{n=0}^{N} T_n*S_n}{\sum_{n=0}^{N} T_n}
\end{equation}

@@

Pattern discovery involves the identification of musical patterns (i.e. short fragments or melodic ideas that repeat at least twice) both from audio and symbolic representations.
The metrics used to evaluation pattern discovery systems attempt to quantify the ability of the algorithm to not only determine the presents pattern in a piece, but also to find all of their occurrences.
Given the novelty of this task (the first year it appeared in MIREX was 2013), the evaluation metrics are likely to be modified in further editions.
Nonetheless, Collins compiled all previously existent metrics and proposed novel ones \cite{Collins2013}, which resulted in 19 different scores, each one implemented in \mireval{}:
\textbf{Standard F-measure, Precision, and Recall}, where an estimated prototype pattern is considered correct only if it matches (up to translation) a reference prototype pattern;
\textbf{Establishment F-measure, Precision, and Recall}, which computes the number of reference patterns that were successfully found, no matter how many occurrences were found;
\textbf{Occurrence F-measure, Precision, and Recall}, which measures whether an algorithm is able to retrieve all occurrences of a pattern;
\textbf{Three-layer F-measure, Precision, and Recall}, which capture both the establishment of the patterns and the occurrence retrieval in a single set of scores;
and the \textbf{First $N$ patterns metrics}, where the target proportion establishment recall and three-layer precision analyzing the first $N$ patterns only, which measures the ability of the algorithm to sort the identified patterns based on their relevance.

>>>>

Despite being one of the oldest MIREX tasks, evaluation methodology and metrics for automatic chord estimation is an ongoing topic of discussion, due to issues with vocabularies, comparison semantics, and other lexicographical challenges unique to the task \cite{pauwels2013evaluating}.
One source of difficulty stems from an inherent subjectivity in ``spelling'' a chord name and the level of detail a human observer can provide in a reference annotation \cite{ni2013understanding}.
As a result, a consensus has yet to be reached regarding the single best approach to comparing two sequences of chord labels, and instead are often compared over a set of rules, i.e Root, Major-Minor, and Sevenths, with or without inversions.

To efficiently compare chords, we first separate a given chord label into a its constituent parts, based on the syntax of \cite{harte2010towards}.
For example, the chord label \texttt{G:maj(6)/5} is mapped to three pieces of information: the root (``G''), the root-invariant active semitones as determined by the quality shorthand (``maj'') and scale degrees (``6''), and the bass interval (``5'').

Based on this representation, we can define our interpretation of the five rules used in MIREX 2013\cite{choi2013mirex} to compare an estimated chord label with a reference by the following rules:
\textbf{Root} requires only that the roots are equivalent;
\textbf{Major-Minor} includes Root, and further requires that the active semitones are equivalent subject to the reference chord quality being Maj or min;
\textbf{Sevenths} follows Major-minor, but is instead subject to the reference chord quality being one of Maj, min, Maj7, min7, 7, or minmaj7;
and finally, \textbf{Major-Minor-Inv} and \textbf{Sevenths-Inv} include Major-Minor and Sevenths respectively, but further require that the bass intervals are equivalent subject to the reference bass interval being an active semitone.
The ``subject to...'' conditions above indicate that a comparison is \emph{ignored} during evaluation if the given criteria is not satisfied.

Track-wise scores are computed by weighting each comparison by the duration of its interval, over all intervals in an audio file; stated another way, this is the piecewise continuous-time integral of the equivalence of two chord sequences.
This is achieved by forming the union of the boundaries in each sequence, sampling the labels, and summing the time intervals of the ``correct'' ranges. 
The cumulative score, referred to as \emph{weighted chord symbol recall} (WCSR), is tallied over a set audio files, by discrete summation, where the importance of each score is weighted by the duration of each annotation \cite{choi2013mirex}.

@@

Pattern discovery involves the identification of musical patterns (i.e. short fragments or melodic ideas that repeat at least twice) both from audio and symbolic representations.
The metrics used to evaluation pattern discovery systems attempt to quantify the ability of the algorithm to not only determine the presents pattern in a piece, but also to find all of their occurrences.
Given the novelty of this task (the first year it appeared in MIREX was 2013), the evaluation metrics are likely to be modified in further editions.

Nonetheless, Collins compiled all previously existent metrics and proposed novel ones \cite{Collins2013}, which resulted in 19 different scores, each one implemented in \mireval{}:
\textbf{Standard F-measure, Precision, and Recall}, where an estimated prototype pattern is considered correct only if it matches (up to translation) a reference prototype pattern;
\textbf{Establishment F-measure, Precision, and Recall}, which computes the number of reference patterns that were successfully found, no matter how many occurrences were found;
\textbf{Occurrence F-measure, Precision, and Recall}, which measures whether an algorithm is able to retrieve all occurrences of a pattern;
\textbf{Three-layer F-measure, Precision, and Recall}, which capture both the establishment of the patterns and the occurrence retrieval in a single set of scores;
and the \textbf{First $N$ patterns metrics}, where the target proportion establishment recall and three-layer precision analyzing the first $N$ patterns only, which measures the ability of the algorithm to sort the identified patterns based on their relevance.
